---
title: "R Code Lawson et al 2023 - Fish Communities"
author: "Lauren Lawson"
date: "2023-10-12"
output: html_document
---

---
#Packages
```{r setup, include=FALSE}
library(readxl)
library(tidyverse)
library(vegan)
library(ggplot2)
library(viridis)
library(dplyr)
library(lme4)
library(car)
library(AICcmodavg)
library(MuMIn)
library(adespatial)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(ggplot2)
```


#Temporal Beta Diversity Index
##Calculating Temporal Beta Diversity Index
```{r}
#Calculates TBI using species by site matrix from first time period and second time period
z <- TBI(pivot_first_m, pivot_last_m, method = "%difference", BCD = TRUE, nperm = 9999, test.BC = TRUE, pa.tr= FALSE) 

#writes in the names of the sites by assigning station names in alphabetical order which the matrices are organized in 
letter.station <- substr(TBI.results$StationName, 1, 1)

#merging datasets to include station name
Stations <- first_last_fish[,1]
Stations <- Stations %>% 
  distinct()

#creates table with TBI results
TBI <- as.data.frame(z[[1]])
p.TBI <- as.data.frame(z[[2]])
BCD <- as.data.frame(z[[4]])
p.adjusted <- as.data.frame(z[[3]])

#binds to station names for TBI results 
TBI.results <- cbind(Stations, TBI, p.TBI, p.adjusted, BCD)

colnames(TBI.results) <- c("Station", "TBI", "p.TBI", "p.adjusted", "Losses", "Gains", "D=(B+C)/(2A+B+B)", "Change" )

View(TBI.results)
```
##Plotting BC Plot based on TBI
```{r}
#this plots the BC plot data with design features
bcplot %>% 
  ggplot(aes(x= Loss, y = Gain, fill = Watershed, shape = Change, size = TBI, color = Watershed))
  + geom_point(alpha = .65, color = "black") +
  scale_fill_manual(values=cbPalette) +
  scale_shape_manual(values = c(21,22) ) +
  scale_size(range = c(2, 7)) + 
  guides(fill = guide_legend(override.aes=list(shape=21, size = 5))) +
  guides(shape = guide_legend(override.aes= list(size = 5))) +
  geom_hline(yintercept = 0, linetype = "solid", color = "grey") +
  geom_vline(xintercept = 0, linetype = "solid", color = "grey") +
  geom_abline(aes(intercept=0,slope=1), color = "black", linetype = "solid") +
  geom_abline(aes(intercept = .1054002, slope = 1),linetype = "dashed", color = "red") 
  + xlab("Species losses (B)") + ylab("Species gains (C)") +
  xlim(0, 1) +
  ylim(0,1) +
  theme_bw() +
  theme(aspect.ratio = 1) +
  annotate("text", x=.4, y=.75, label= "Gains > Losses", fontface = "bold") +
  annotate("text", x=.75, y=.25, label= "Losses > Gains", fontface = "bold") +
  annotate('text', x = .90, y = .865, label = '1-1 line', size = 4, angle='45') +
  annotate('text', x = .80, y = .95, label = 'centroid line', size = 4, angle='45') +
  annotate("text", x=.1, y=.85, label= "*", fontface = "bold", color = "black", size = 6) +
  annotate("text", x=0.93493151, y=0.003424658, label= "*", fontface = "bold", color = "black",    size = 6) +
  annotate("text", x=0.05196850, y=0.875590551, label= "*", fontface = "bold", color = "black",    size = 6) +
  annotate("text", x=0.16326531, y=0.75102041, label= "*", fontface = "bold", color = "black",     size = 6) +
  annotate("text", x=0.80172414, y=0.112068966, label= "*", fontface = "bold", color = "black",    size = 6) +
  annotate("text", x=0.90163934, y=0.010928962, label= "*", fontface = "bold", color = "black",    size = 6) +
  annotate("text", x=0.16458853, y=0.715685786, label= "*", fontface = "bold", color = "black",    size = 6) 
```
##Modelling
###Temporal Beta Diversity
####Fixed effects models
```{r}
#NO interactions global model
m1 <- lmer(TBI ~  Urban.2000.UC + Percent.change.urban + Wetland.2000.UC+ Percent.change.wetland + Woodland.2000.UC + Percent.change.woodland + DCIs1980 + DCI.diff + (1|Watershed), REML = F, data = TBI.predictors)
Cand.models[[1]] <- m1 

#land use
m2 <- lmer(TBI ~  Urban.2000.UC + Percent.change.urban + Wetland.2000.UC+ Percent.change.wetland + Woodland.2000.UC + Percent.change.woodland + (1|Watershed), REML = FALSE, data = TBI.predictors)
Cand.models[[2]] <- m2

#DCI
m3 <- lmer(TBI ~ DCIs1980 + DCI.diff + (1|Watershed), REML = FALSE, data = TBI.predictors)
Cand.models[[3]] <- m3

#Urban
m4 <- lmer(TBI ~  Urban.2000.UC + Percent.change.urban + (1|Watershed), REML = F, data = TBI.predictors)
Cand.models[[4]] <- m4 

#Wetland
m5 <- lmer(TBI ~  Wetland.2000.UC+ Percent.change.wetland + (1|Watershed), REML = F, data = TBI.predictors)
Cand.models[[5]] <- m5 

#Woodland
m6<- lmer(TBI ~   Woodland.2000.UC + Percent.change.woodland + (1|Watershed), REML = F, data = TBI.predictors)
Cand.models[[6]] <- m6 

#m7 <- lmer(TBI ~ (1|Watershed), REML = F, data = TBI.predictors)
#Cand.models[[7]] <- m7

Modnames <- paste("model", 1:length(Cand.models), sep = " ")
aictab(cand.set = Cand.models, modnames = Modnames, sort = TRUE)
rich.aic <- as.data.frame.matrix(aictab(cand.set = Cand.models, modnames = Modnames, sort = TRUE),digits = 4, LL = TRUE)
```
####Model averaging code and plot
```{r}
#this selects the top TBI models to model average them
top.tbi.6 <- lmer(TBI ~   Woodland.2000.UC + Percent.change.woodland + (1|Watershed), REML = T, data = TBI.predictors)

top.tbi.5 <- lmer(TBI ~  Wetland.2000.UC+ Percent.change.wetland + (1|Watershed), REML = T, data = TBI.predictors)

top.tbi.4 <- lmer(TBI ~  Urban.2000.UC + Percent.change.urban + (1|Watershed), REML = T, data = TBI.predictors)

top.TBI.list <- list(top.tbi.6, top.tbi.5, top.tbi.4)

#model averaging
avg.tbi <- model.avg(top.TBI.list)

#creating dataset to plot nicely
avg.tbi.coef <- as.data.frame(avg.tbi$coefficients)
avg.tbi.coef <- avg.tbi.coef %>% 
  t()
con.tbi <- confint(avg.tbi, full = F)
beta <- cbind(avg.tbi.coef, con.tbi)
beta<- as.data.frame(beta)
rownames(beta) <- c("(Intercept)", "Woodland T1","Woodland loss %", "Wetland T1", "Weltand loss %", "Anthro. T1", "Anthro. Intensif. %")
beta <- cbind(Variable = rownames(beta), beta)
colnames(beta) <- c("Variable", "Full", "Subset", "lower.con", "upper.con")

#plotting TBI model averaged values
tbi.averaged.plot <- beta %>% 
  ggplot(aes(x = Subset, y = Variable)) +
  geom_point(size = 2.5) +
  theme_bw() +
  scale_x_continuous(limits = c(-.2, .2), breaks = seq(-.2, .2, .1)) +
  theme(legend.position = "none", aspect.ratio = 1) +
  geom_linerange(aes(y = Variable, xmin = lower.con, xmax = upper.con, linetype = 'dashed')) +
  ggtitle('TBI') +
  xlab('Averaged Estimate') +
  geom_vline(xintercept = 0, linetype = "dashed") 

tbi.averaged.plot
```

###Richness
####Fixed effects
```{r}
Cand.models <- list()

m1 <- lmer(Rich.change ~  Urban.2000.UC + Percent.change.urban + Wetland.2000.UC+ Percent.change.wetland + Woodland.2000.UC + Percent.change.woodland + DCIs1980 + DCI.diff + (1|Watershed), REML = F, data = trca_standardized2)
Cand.models[[1]] <- m1 

#land use
m2 <- lmer(Rich.change ~  Urban.2000.UC + Percent.change.urban + Wetland.2000.UC+ Percent.change.wetland + Woodland.2000.UC + Percent.change.woodland + (1|Watershed), REML = FALSE, data = trca_standardized2)
Cand.models[[2]] <- m2

#DCI
m3 <- lmer(Rich.change ~ DCIs1980 + DCI.diff + (1|Watershed), REML = FALSE, data = trca_standardized2)
Cand.models[[3]] <- m3

#Urban
m4 <- lmer(Rich.change ~  Urban.2000.UC + Percent.change.urban + (1|Watershed), REML = F, data = trca_standardized2)
Cand.models[[4]] <- m4 

#Wetland
m5 <- lmer(Rich.change ~  Wetland.2000.UC+ Percent.change.wetland + (1|Watershed), REML = F, data = trca_standardized2)
Cand.models[[5]] <- m5 

#Woodland
m6<- lmer(Rich.change ~   Woodland.2000.UC + Percent.change.woodland + (1|Watershed), REML = F, data = trca_standardized2)
Cand.models[[6]] <- m6

Modnames <- paste("model", 1:length(Cand.models), sep = " ")
aictab(cand.set = Cand.models, modnames = Modnames, sort = TRUE)
rich.aic <- as.data.frame.matrix(aictab(cand.set = Cand.models, modnames = Modnames, sort = TRUE),digits = 4, LL = TRUE)
```
####Model averaging 
```{r}
#Wetland
richness.1 <- lmer(Rich.change ~  Wetland.2000.UC+ Percent.change.wetland + (1|Watershed), REML = T, data = trca_standardized)
#DCI
richness.2 <- lmer(Rich.change ~ DCIs1980 + DCI.diff + (1|Watershed), REML = T, data = trca_standardized)

#top models list
rich.top <- list(richness.1, richness.2)

#model averaging
sum.rich <- model.avg(rich.top)
sum.rich.coef <- as.data.frame(sum.rich$coefficients)
sum.rich.coef <- sum.rich.coef %>% 
  t()

#confidence intervals
con <- confint(sum.rich, full = F) #these are the subset estimates
#binding estimates and confidence intervals
k <- cbind(sum.rich.coef, con)
k <- as.data.frame(k)
#renaming rows
rownames(k) <- c("(Intercept)", "Wetland T1","Wetland loss % ","DCI T1", "DCI Δ")
#making column for variables names
k <- cbind(Variable = rownames(k), k)
#renaming columns
colnames(k) <- c("Variable", "Full", "Subset", "lower.con", "upper.con")
```
####Model avg estimate plot
```{r}
rich.averaged.plot <- k %>% 
  ggplot(aes(x = Subset, y = Variable)) +
  geom_point(size = 2.5) +
  theme_bw() +
  scale_x_continuous(limits = c(-2, 2), breaks = seq(-2, 2, .5)) +
  theme(legend.position = "none", aspect.ratio = 1) +
  geom_linerange(aes(y = Variable, xmin = lower.con, xmax = upper.con,    
                     linetype = 'dashed')) +
  ggtitle('Richness') +
  xlab('Averaged Estimate') + 
  geom_vline(xintercept = 0, linetype = "dashed") 

rich.averaged.plot
```

###Evenness
####Fixed effects models
```{r}
Cand.models <- list()

#NO interactions global models
m1 <- lmer(Even.change ~  Urban.2000.UC + Percent.change.urban + Wetland.2000.UC+ Percent.change.wetland + Woodland.2000.UC + Percent.change.woodland + DCIs1980 + DCI.diff + (1|Watershed), REML = F, data = trca_standardized)
Cand.models[[1]] <- m1 

#land use
m2 <- lmer(Even.change ~  Urban.2000.UC + Percent.change.urban + Wetland.2000.UC+ Percent.change.wetland + Woodland.2000.UC + Percent.change.woodland + (1|Watershed), REML = FALSE, data = trca_standardized)
Cand.models[[2]] <- m2

#DCI
m3 <- lmer(Even.change ~ DCIs1980 + DCI.diff + (1|Watershed), REML = FALSE, data = trca_standardized)
Cand.models[[3]] <- m3

#Urban
m4 <- lmer(Even.change ~  Urban.2000.UC + Percent.change.urban + (1|Watershed), REML = F, data = trca_standardized)
Cand.models[[4]] <- m4 

#Wetland
m5 <- lmer(Even.change ~  Wetland.2000.UC+ Percent.change.wetland + (1|Watershed), REML = F, data = trca_standardized)
Cand.models[[5]] <- m5 

#Woodland
m6<- lmer(Even.change ~   Woodland.2000.UC + Percent.change.woodland + (1|Watershed), REML = F, data = trca_standardized)
Cand.models[[6]] <- m6 

#AIC
Modnames <- paste("model", 1:length(Cand.models), sep = " ")
aictab(cand.set = Cand.models, modnames = Modnames, sort = TRUE)
rich.aic <- as.data.frame.matrix(aictab(cand.set = Cand.models, modnames = Modnames, sort = TRUE),digits = 4, LL = TRUE)
```
####Model averaging
```{r}
top.even.5 <- lmer(Even.change ~  Wetland.2000.UC+ Percent.change.wetland + (1|Watershed), REML = T, data = trca_standardized)

top.even.6 <- lmer(Even.change ~   Woodland.2000.UC + Percent.change.woodland + (1|Watershed), REML = T, data = trca_standardized)

top.even.4 <- lmer(Even.change ~  Urban.2000.UC + Percent.change.urban + (1|Watershed), REML = T, data = trca_standardized)

top.even.list <- list(top.even.5, top.even.6, top.even.4)

avg.even <- model.avg(top.even.list)
avg.even.coef <- as.data.frame(avg.even$coefficients)
avg.even.coef <- avg.even.coef %>% 
  t()
con.even <- confint(avg.even, full = F)
e <- cbind(avg.even.coef, con.even)
e<- as.data.frame(e)
rownames(e) <- c("(Intercept)", "Wetland T1","Wetland loss %", "Woodland T1", "Woodland loss %", "Anthro. T1", "Anthro. Intensif. %")
e <- cbind(Variable = rownames(e), e)
colnames(e) <- c("Variable", "Full", "Subset", "lower.con", "upper.con")
```
####Model avg estimate plot
```{r}
even.averaged.plot <- e %>% 
  ggplot(aes(x = Subset, y = Variable)) +
  geom_point(size = 2.5) +
  theme_bw() +
  scale_x_continuous(limits = c(-.2, .2), breaks = seq(-.2, .2, .1)) +
  theme(legend.position = "none", aspect.ratio = 1) +
  geom_linerange(aes(y = Variable, xmin = lower.con, xmax = upper.con, linetype = 'dashed')) +
  ggtitle('Pielou evenness') +
  xlab('Averaged Estimate') +
  geom_vline(xintercept = 0, linetype = "dashed") 

even.averaged.plot
```

###Shan Diversity
####Fixed effects
```{r}
Cand.models <- list()

#NO interactions global models
m1 <- lmer(Shan.change ~  Urban.2000.UC + Percent.change.urban + Wetland.2000.UC+ Percent.change.wetland + Woodland.2000.UC + Percent.change.woodland + DCIs1980 + DCI.diff + (1|Watershed), REML = F, data = trca_standardized)
Cand.models[[1]] <- m1 

#land use
m2 <- lmer(Shan.change ~  Urban.2000.UC + Percent.change.urban + Wetland.2000.UC+ Percent.change.wetland + Woodland.2000.UC + Percent.change.woodland + (1|Watershed), REML = FALSE, data = trca_standardized)
Cand.models[[2]] <- m2

#DCI
m3 <- lmer(Shan.change ~ DCIs1980 + DCI.diff + (1|Watershed), REML = FALSE, data = trca_standardized)
Cand.models[[3]] <- m3

#Urban
m4 <- lmer(Shan.change ~  Urban.2000.UC + Percent.change.urban + (1|Watershed), REML = F, data = trca_standardized)
Cand.models[[4]] <- m4 

#Wetland
m5 <- lmer(Shan.change ~  Wetland.2000.UC+ Percent.change.wetland + (1|Watershed), REML = F, data = trca_standardized)
Cand.models[[5]] <- m5 

#Woodland
m6<- lmer(Shan.change ~   Woodland.2000.UC + Percent.change.woodland + (1|Watershed), REML = F, data = trca_standardized)
Cand.models[[6]] <- m6 

Modnames <- paste("model", 1:length(Cand.models), sep = " ")
aictab(cand.set = Cand.models, modnames = Modnames, sort = TRUE)
rich.aic <- as.data.frame.matrix(aictab(cand.set = Cand.models, modnames = Modnames, sort = TRUE),digits = 4, LL = TRUE)
```
####Model averaging
```{r}
#DCI
shan.3 <- lmer(Shan.change ~ DCIs1980 + DCI.diff + (1|Watershed), REML = T, data = trca_standardized)
#Urban
shan.4 <- lmer(Shan.change ~  Urban.2000.UC + Percent.change.urban + (1|Watershed), REML = T, data = trca_standardized)
#Wetland
shan.5 <- lmer(Shan.change ~  Wetland.2000.UC+ Percent.change.wetland + (1|Watershed), REML = T, data = trca_standardized)
#Woodland
shan.6 <- lmer(Shan.change ~   Woodland.2000.UC + Percent.change.woodland + (1|Watershed), REML = T, data = trca_standardized)

#top models list
shan.top <- list(shan.3, shan.4, shan.5, shan.6)

#model averaging
sum.shan <- model.avg(shan.top)
sum.shan.coef <- as.data.frame(sum.shan$coefficients)
sum.shan.coef <- sum.shan.coef %>% 
  t()

#confidence intervals
con <- confint(sum.shan, full = F) #these are the subset estimates
#binding estimates and confidence intervals
k <- cbind(sum.shan.coef, con)
k <- as.data.frame(k)
#renaming rows
rownames(k) <- c("(Intercept)", "DCI T1","DCI Δ","Wetland T1", "Wetland loss %", "Anthro. T1", "Anthro. Intensif. %", "Woodland T1", "Woodland loss %")
#making column for variables names
k <- cbind(Variable = rownames(k), k)
#renaming columns
colnames(k) <- c("Variable", "Full", "Subset", "lower.con", "upper.con")
```

####Model avg estimate plot
```{r}
#plotting estimates!
shan.averaged.plot <- k %>% 
  ggplot(aes(x = Subset, y = Variable)) +
  geom_point(size = 2.5) +
  theme_bw() +
  scale_x_continuous(limits = c(-.25, .25), breaks = seq(-.25, .25, .1)) +
  theme(legend.position = "none", aspect.ratio = 1) +
  geom_linerange(aes(y = Variable, xmin = lower.con, xmax = upper.con, linetype = 'dashed')) +
  ggtitle('Shannon diversity') +
  xlab('Averaged Estimate') + 
  geom_vline(xintercept = 0, linetype = "dashed") 
shan.averaged.plot
```
##Panel plot for model average results
```{r}
gridExtra::grid.arrange(rich.averaged.plot 
, shan.averaged.plot, even.averaged.plot, tbi.averaged.plot , nrow = 2, ncol = 2)
```

#T \tests
##Full dataset
```{r}
t <- tpaired.krandtest(pivot_first_m, pivot_last_m, nperm = 9999, list.all = FALSE)
summary(z)
View(t[[1]])
full.t <- t[[1]]
species <- rownames(full.t)
species <- as.data.frame(species)

p.adjust(t$t.tests$p.perm,method = "holm")

y <- p.adjust(t$t.tests$p.perm,method = "holm")
o <- as.data.frame(y)
p <- bind_cols(species, o)
paired.full <- bind_cols(full.t, o)

paired.full <- paired.full %>% 
    rename("p.holm.adj" = "y")
```
##Watersheds
###Don River
```{r}
#first time period 
Matrix.Don.first <- Matrix_site_first %>% filter(Watershed == "Don River") 
Matrix.Don.first <- Matrix.Don.first[,c(4:ncol(Matrix.Don.first))]

#second time period
Matrix.Don.last <- Matrix_site_last %>% filter(Watershed == "Don River") 
Matrix.Don.last <- Matrix.Don.last[,c(4:ncol(Matrix.Don.last))]

#t.tests
t <- tpaired.krandtest(Matrix.Don.first, Matrix.Don.last, nperm = 9999, list.all = FALSE)
full.t <- t[[1]]
species <- rownames(full.t)
species <- as.data.frame(species)

#adjusted p values by holm method
y <- p.adjust(t$t.tests$p.perm,method = "holm")
o <- as.data.frame(y)
p <- bind_cols(species, o)
paired.full <- bind_cols(full.t, o)

paired.full.DR <- paired.full %>% 
    rename("p.holm.adj" = "y")
```
###Etobicoke Creek
```{r}
Matrix.EC.first <- Matrix_site_first %>% filter(Watershed == "Etobicoke Creek") 
Matrix.EC.first <- Matrix.EC.first[,c(4:ncol(Matrix.EC.first))]

#second time period
Matrix.EC.last <- Matrix_site_last %>% filter(Watershed == "Etobicoke Creek") 
Matrix.EC.last <- Matrix.EC.last[,c(4:ncol(Matrix.EC.last))]

#paired.t.test
t <- tpaired.krandtest(Matrix.EC.first, Matrix.EC.last, nperm = 9999, list.all = FALSE)
full.t <- t[[1]]
species <- rownames(full.t)
species <- as.data.frame(species)
#adjusted p values
p.adjust(t$t.tests$p.perm,method = "holm")

#merging for datasets
y <- p.adjust(t$t.tests$p.perm,method = "holm")
o <- as.data.frame(y)
p <- bind_cols(species, o)
paired.full <- bind_cols(full.t, o)

paired.full.EC <- paired.full %>% 
    rename("p.holm.adj" = "y")
```
###Highland Creek
```{r}
Matrix.HC.first <- Matrix_site_first %>% filter(Watershed == "Highland Creek") 
Matrix.HC.first <- Matrix.HC.first[,c(4:ncol(Matrix.HC.first))]

#second time period
Matrix.HC.last <- Matrix_site_last %>% filter(Watershed == "Highland Creek") 
Matrix.HC.last <- Matrix.HC.last[,c(4:ncol(Matrix.HC.last))]

#paired.t.test
t <- tpaired.krandtest(Matrix.HC.first, Matrix.HC.last, nperm = 9999, list.all = FALSE)
full.t <- t[[1]]
species <- rownames(full.t)
species <- as.data.frame(species)
#adjusted p values
p.adjust(t$t.tests$p.perm,method = "holm")

#merging for datasets
y <- p.adjust(t$t.tests$p.perm,method = "holm")
o <- as.data.frame(y)
p <- bind_cols(species, o)
paired.full <- bind_cols(full.t, o)

paired.full.HC <- paired.full %>% 
    rename("p.holm.adj" = "y")
```

###Mimico Creek
```{r}
Matrix.MC.first <- Matrix_site_first %>% filter(Watershed == "Mimico Creek") 
Matrix.MC.first <- Matrix.MC.first[,c(4:ncol(Matrix.MC.first))]

#second time period
Matrix.MC.last <- Matrix_site_last %>% filter(Watershed == "Mimico Creek") 
Matrix.MC.last <- Matrix.MC.last[,c(4:ncol(Matrix.MC.last))]

t <- tpaired.krandtest(Matrix.MC.first, Matrix.MC.last, nperm = 9999, list.all = FALSE)
full.t <- t[[1]]
species <- rownames(full.t)
species <- as.data.frame(species)
#adjusted p values
p.adjust(t$t.tests$p.perm,method = "holm")

#merging for datasets
y <- p.adjust(t$t.tests$p.perm,method = "holm")
o <- as.data.frame(y)
p <- bind_cols(species, o)
paired.full <- bind_cols(full.t, o)

paired.full.MC <- paired.full %>% 
    rename("p.holm.adj" = "y")
```
###Rouge River
```{r}
Matrix.RR.first <- Matrix_site_first %>% filter(Watershed == "Rouge River") 
Matrix.RR.first <- Matrix.RR.first[,c(4:ncol(Matrix.RR.first))]

#second time period
Matrix.RR.last <- Matrix_site_last %>% filter(Watershed == "Rouge River") 
Matrix.RR.last <- Matrix.RR.last[,c(4:ncol(Matrix.RR.last))]

#paired t test
t <- tpaired.krandtest(Matrix.RR.first, Matrix.RR.last, nperm = 9999, list.all = FALSE)
full.t <- t[[1]]
species <- rownames(full.t)
species <- as.data.frame(species)
#adjusted p values
p.adjust(t$t.tests$p.perm,method = "holm")

#adjusted p values
y <- p.adjust(t$t.tests$p.perm,method = "holm")
o <- as.data.frame(y)
p <- bind_cols(species, o)
paired.full <- bind_cols(full.t, o)

#merge the two
paired.full.RR <- paired.full %>% 
    rename("p.holm.adj" = "y")
```
##Strahler
###2
```{r}
Matrix.2.first <- Matrix_site_first %>% filter(Strahler == "2") 
Matrix.2.first <- Matrix.2.first[,c(4:ncol(Matrix.2.first))]

#second time period
Matrix.2.last <- Matrix_site_last %>% filter(Strahler == "2") 
Matrix.2.last <- Matrix.2.last[,c(4:ncol(Matrix.2.last))]

t <- tpaired.krandtest(Matrix.2.first, Matrix.2.last, nperm = 9999, list.all = FALSE)
full.t <- t[[1]]
species <- rownames(full.t)
species <- as.data.frame(species)


p.adjust(t$t.tests$p.perm,method = "holm")
y <- p.adjust(t$t.tests$p.perm,method = "holm")
o <- as.data.frame(y)
p <- bind_cols(species, o)
paired.full <- bind_cols(full.t, o)

paired.full.2 <- paired.full %>% 
    rename("p.holm.adj" = "y")
```
###3
```{r}
Matrix.3.first <- Matrix_site_first %>% filter(Strahler == "3") 
Matrix.3.first <- Matrix.3.first[,c(4:ncol(Matrix.3.first))]

#second time period
Matrix.3.last <- Matrix_site_last %>% filter(Strahler == "3") 
Matrix.3.last <- Matrix.3.last[,c(4:ncol(Matrix.3.last))]

t <- tpaired.krandtest(Matrix.3.first, Matrix.3.last, nperm = 9999, list.all = FALSE)
full.t <- t[[1]]
species <- rownames(full.t)
species <- as.data.frame(species)

#adjusting p values
p.adjust(t$t.tests$p.perm,method = "holm")
y <- p.adjust(t$t.tests$p.perm,method = "holm")
o <- as.data.frame(y)
p <- bind_cols(species, o)
paired.full <- bind_cols(full.t, o)

paired.full.3 <- paired.full %>% 
    rename("p.holm.adj" = "y")
```
###4 
```{r}
Matrix.4.first <- Matrix_site_first %>% filter(Strahler == "4") 
Matrix.4.first <- Matrix.4.first[,c(4:ncol(Matrix.4.first))]

#second time period
Matrix.4.last <- Matrix_site_last %>% filter(Strahler == "4") 
Matrix.4.last <- Matrix.4.last[,c(4:ncol(Matrix.4.last))]

t <- tpaired.krandtest(Matrix.4.first, Matrix.4.last, nperm = 9999, list.all = FALSE)
full.t <- t[[1]]
species <- rownames(full.t)
species <- as.data.frame(species)

p.adjust(t$t.tests$p.perm,method = "holm")
y <- p.adjust(t$t.tests$p.perm,method = "holm")
o <- as.data.frame(y)
p <- bind_cols(species, o)
paired.full <- bind_cols(full.t, o)

paired.full.4 <- paired.full %>% 
    rename("p.holm.adj" = "y")
```
###5
```{r}
Matrix.5.first <- Matrix_site_first %>% filter(Strahler == "5") 
Matrix.5.first <- Matrix.5.first[,c(4:ncol(Matrix.5.first))]

#second time period
Matrix.5.last <- Matrix_site_last %>% filter(Strahler == "5") 
Matrix.5.last <- Matrix.5.last[,c(4:ncol(Matrix.5.last))]

t <- tpaired.krandtest(Matrix.5.first, Matrix.5.last, nperm = 9999, list.all = FALSE)
full.t <- t[[1]]
species <- rownames(full.t)
species <- as.data.frame(species)

p.adjust(t$t.tests$p.perm,method = "holm")
y <- p.adjust(t$t.tests$p.perm,method = "holm")
o <- as.data.frame(y)
p <- bind_cols(species, o)
paired.full <- bind_cols(full.t, o)

paired.full.5 <- paired.full %>% 
    rename("p.holm.adj" = "y")
```
###6
```{r}
Matrix.6.first <- Matrix_site_first %>% filter(Strahler == "6") 
Matrix.6.first <- Matrix.6.first[,c(4:ncol(Matrix.6.first))]

#second time period
Matrix.6.last <- Matrix_site_last %>% filter(Strahler == "6") 
Matrix.6.last <- Matrix.6.last[,c(4:ncol(Matrix.6.last))]

t <- tpaired.krandtest(Matrix.6.first, Matrix.6.last, nperm = 9999, list.all = FALSE)
full.t <- t[[1]]
species <- rownames(full.t)
species <- as.data.frame(species)

p.adjust(t$t.tests$p.perm,method = "holm")
y <- p.adjust(t$t.tests$p.perm,method = "holm")
o <- as.data.frame(y)
p <- bind_cols(species, o)
paired.full <- bind_cols(full.t, o)

paired.full.6 <- paired.full %>% 
    rename("p.holm.adj" = "y")

```

##High TBI 
###All
```{r}
Matrix.signif.first <- Matrix_site_first %>% filter(StationName == "DN011WM"| StationName =="HL005WM" |StationName == "MM002WM"|StationName == "RG019WM"|StationName == "DN010WMb"| StationName == "EC001WM" | StationName == "EC010WM")
Matrix.signif.first  <- Matrix.signif.first[,c(4:ncol(Matrix.signif.first))]

Matrix.signif.last <- Matrix_site_last %>%  filter(StationName == "DN011WM"| StationName =="HL005WM" |StationName == "MM002WM"|StationName == "RG019WM"|StationName == "DN010WMb"| StationName == "EC001WM" | StationName == "EC010WM" )
Matrix.signif.last  <- Matrix.signif.last[,c(4:ncol(Matrix.signif.last))]

t <- tpaired.krandtest(Matrix.signif.first, Matrix.signif.last, nperm = 9999, list.all = FALSE)
full.t <- t[[1]]
species <- rownames(full.t)
species <- as.data.frame(species)

p.adjust(t$t.tests$p.perm,method = "holm")
y <- p.adjust(t$t.tests$p.perm,method = "holm")
o <- as.data.frame(y)
p <- bind_cols(species, o)
paired.full <- bind_cols(full.t, o)

paired.full <- paired.full %>% 
    rename("p.holm.adj" = "y")
```

###Gains
```{r}
Matrix.signif.first.gains <- Matrix_site_first %>% filter(StationName == "DN011WM"| StationName =="HL005WM" |StationName == "MM002WM" | StationName == "EC010WM")
Matrix.signif.first.gains  <- Matrix.signif.first.gains[,c(4:ncol(Matrix.signif.first.gains))]

Matrix.signif.last.gains <- Matrix_site_last %>%  filter(StationName == "DN011WM"| StationName =="HL005WM" |StationName == "MM002WM" | StationName == "EC010WM")
Matrix.signif.last.gains  <- Matrix.signif.last.gains[,c(4:ncol(Matrix.signif.last.gains))]

t <- tpaired.krandtest(Matrix.signif.first.gains, Matrix.signif.last.gains, nperm = 9999, list.all = FALSE)
full.t <- t[[1]]
species <- rownames(full.t)
species <- as.data.frame(species)

p.adjust(t$t.tests$p.perm,method = "holm")
y <- p.adjust(t$t.tests$p.perm,method = "holm")
o <- as.data.frame(y)
p <- bind_cols(species, o)
paired.gains<- bind_cols(full.t, o)

paired.gains <- paired.gains %>% 
    rename("p.holm.adj" = "y")
```

###Losses
```{r}
Matrix.signif.first.losses <- Matrix_site_first %>% filter(StationName == "DN011WM"| StationName =="HL005WM" |StationName == "MM002WM")
Matrix.signif.first.losses  <- Matrix.signif.first.losses[,c(4:ncol(Matrix.signif.first.losses))]

Matrix.signif.last.losses <- Matrix_site_last %>%  filter(StationName == "DN011WM"| StationName =="HL005WM" |StationName == "MM002WM")
Matrix.signif.last.losses  <- Matrix.signif.last.losses[,c(4:ncol(Matrix.signif.last.losses))]

t <- tpaired.krandtest(Matrix.signif.first.losses, Matrix.signif.last.losses, nperm = 9999, list.all = FALSE)
full.t <- t[[1]]
species <- rownames(full.t)
species <- as.data.frame(species)

p.adjust(t$t.tests$p.perm,method = "holm")
y <- p.adjust(t$t.tests$p.perm,method = "holm")
o <- as.data.frame(y)
p <- bind_cols(species, o)
paired.losses <- bind_cols(full.t, o)

paired.losses <- paired.losses %>% 
    rename("p.holm.adj" = "y")
```

#TBI presence absence
```{r}
pa <- TBI(pivot_first_m, pivot_last_m, method = "%difference", pa.tr = TRUE, BCD = TRUE, nperm = 9999, test.BC = TRUE) 
pa
pa[[1]]

plot(pa)

pa.data <- pa[1]

TBI.pa <- as.data.frame(pa[1])
p.TBI.pa <- as.data.frame(pa[2])
p.adjusted.pa <- as.data.frame(pa[3])
BCD.pa <- as.data.frame(pa[4])

TBI.results.pa <- cbind(Stations, TBI.pa, p.TBI.pa, p.adjusted.pa, BCD.pa)

colnames(TBI.results.pa) <- c("Station", "TBI", "p.TBI", "p.adjusted", "Losses", "Gains", "D=(B+C)/(2A+B+B)", "Change" )
```
